Fast algebraic filtering of surfaces from 3D medical images with Julia

### 2019-07-07 src/implementation.tex
new examples added and text with statistic

@@

>>>>

\begin{figure}[htbp]
\includegraphics[width=0.99\textwidth]{figs/schema_horizontal.pdf} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\caption{Workflow of LAR-SURF algorithm}
\label{fig:schema}
\end{figure}

@@

The size of boundary matrix is critical parameter of LAR-SURF method. To determine optimal size of boundary matrix the experiment on artifical data was performed (Fig.  \ref{fig:bm_size_tesla}). Size of experimental data is set to $512\times512\times512$ and it is derived from typical size of Computed Tomography medical images. Computation is done on Tesla DGX-1 machine.

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figs/bm_size_tesla.pdf} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\caption{Time requirements of LAR-SURF filter used on artifical with different size of boundary matrix}
\label{fig:bm_size_tesla}
\end{figure}

To compare time requirements of LAR-SURF with Marching Cubes implemented in Python we performed experiment on Ircadb dataset \cite{ircad}. Dataset contain 20 Computed Tomography images (see table \ref{tab:ircad1}) with xy-resolution from 0.56 mm to 0.87 mm and z-resolution from 1.0 mm to 4.0 mm. The number of slices is each series varies from 74 to 260 and size of each slice is $512\times512$. Dataset contain manually segmented liver, portal vein and other structures. We performed surface extraction of liver with Marching Cubes and LAR-SURF. Time required for computation can be seen on figure \ref{fig:ircad_comparison}.

Based on t-test with $\alpha=0.99$, $p=\input{input/ircad_pvalue}$ and 
$s=\input{input/ircad_statistics}$ it can be shown that the mean of time consumed by LAR-SURF is significantly lower from time consumed by Marching Cubes.

\begin{figure}
\centering
\includegraphics[width=0.99\textwidth]{figs/ircad_comparison.pdf} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\caption{Time requirements of LAR-SURF filter and Marching Cubes on Ircad dataset. Error bars shows the 95\% confidence interval}
\label{fig:ircad_comparison}
\end{figure}
